Proposed Solution

### 2017-01-25 CAV17/secs/intro.tex
stuff

>>>>

Configuration errors (also known as misconfigurations) have become
one of the major causes of system failures, resulting in security vulnerabilities,
application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. Recently, there was a problem in accessing  
Facebook and Instagram~\cite{mashableNews}, 
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In a recent software system failures study~\cite{yin11anempirical},
researchers revealed that about 31\% of system failures were caused by 
configuration errors, which is higher than the percentage of
failures resulting from program bugs (20\%).

The systems research community has recognized this as an important
problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code. In this paper we propose
a framework for automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen.

Configuration errors were
reported to be the largest fraction of failures in storage systems in a 2014 industry
survey~\cite{yin11anempirical}.
